Functional Pearl: the Proof Search Monad

### 2015-10-12 paper/main.tex
Better motivation + qed combinator.

\usepackage{tabularx}
\usepackage{listings}
  \def\li{\lstinline}
  \lstset{
    language=caml,
    flexiblecolumns=false,
    showstringspaces=false,
    basicstyle=\ttfamily,
    framesep=5pt,
    numberstyle=\tiny,
    numbersep=5pt,
    escapeinside={(*}{*)},
    morekeywords={above,abstract,adopts,alias,and,as,assert,begin,below,builtin,consumes,data,do,downto,duplicable,dynamic,else,empty,end,exclusive,explain,fact,fail,flex,for,from,fun,give,if,in,let,match,mutable,open,pack,perm,preserving,rec,take,taking,then,to,type,unknown,val,value,while,with,witness},
    deletekeywords={value},
  }
\usepackage{minted}
  \newminted[ocaml]{ocaml}{mathescape,fontsize=\small}
\usepackage{mathpartir}
  % Improvements to Didier's mathpartir package: make all rule names and
  % references use textsc, and also make references to rules done using the \Rule
  % command clickable in a PDF.
  \let\TirName\textsc
  \renewcommand{\RefTirName}[1]{\hypertarget{#1}{\TirName {#1}}}
  \renewcommand{\DefTirName}[1]{\hyperlink{#1}{\TirName {#1}}}
  \let\DefRule\RefTirName
  \let\Rule\DefTirName

\newcommand{\fref}[1]{Figure~\ref{fig:#1}}
\newcommand{\R}{\ensuremath{\mathcal{R}}} % Rigid
\newcommand{\f}[1]{\ensuremath{#1^?}} % Bold
\newcommand{\F}{\ensuremath{\mathcal{F}}} % Flexible
\newcommand{\V}{\ensuremath{\mathcal{V}}} % The prefix

@@

\section{A minimal problem}

We consider conjunctions of equalities of the form
$\bigwedge_k x_i = x_j$, that is, conjunctions of
equalities between variables. Some variables are \emph{flexible}, meaning they may be
substituted with other variables. They are typeset as follows: $\f y$.
Rigid variables may not be substituted. They are typeset as follows: $x$. The
problem consists in computing a substitution of \emph{flexible} variables so that
the conjunction evaluates to \li+true+. If no such substitution exists, the
solver outputs nothing.

For instance, one may want to solve: $x = \f y \wedge z = z$.
A solution exists: the solver outputs $\sigma = \{ \f y \mapsto x \}$ as a valid
substitution that solves the input problem. However, if one attempts to solve:
$x = \f y \wedge \f y = z$, the solver fails to find a
proper substitution, and return nothing. Indeed, the first clause demands that
$\f y$ substitutes to $x$, meaning that the second clause becomes $x = z$, which
always evaluates to false ($x$ and $z$ are two distinct rigid variables).

In proof search, rigid variables stem from the right-elimination of universal
quantifiers, or left-elimination of existential quantifiers, which both result
in abstract variables. When left-eliminating a universal quantifier
(respectively right-eliminating an existential quantifier), one must provide an
argument to the type application (resp. an existential witness). If the argument
(resp. the witness) cannot be found on the spot, one typically uses
\emph{flexible variables}, which allow the proof search procedure to
\emph{defer} the choice until a later point in search (where the choice may be
guessed). Flexible variables are thus an \emph{implementation technique}.

In order to simplify the discussion, we skip elimination rules and quantifiers
altogether, and just assume that our input problem contains a combination of
flexible and rigid variables. Furthermore, we assume that any instantiation of a
flexible variable is legal. The only point that matters is that the solver
computes a result which sequenced throughout the proof search.

(The library that we describe here has been used in the implementation of the
Mezzo type-checker. There, the logic (the type system) does have all four
introduction and elimination rules; in the implementation, we used \emph{levels}
to guarantee that only sound instantiation choices are performed. This is,
however, orthogonal to the present discussion; the minimal problem we consider
already conveys all the important points, so we skip quantifiers in the
remainder of the discussion.)

\fref{proof-system} describes a proof search procedure for conjunctions of
equalities. Rules poke at a set of variables $V$ to tell apart rigid variables from
flexible variables. Each rule takes a substitution $\sigma$ as an input, and outputs
an updated substitution $\sigma'$. A variable in $V$ is either a rigid ($x$),
or a flexible ($\f y$).

\Rule{Refl} embodies the reflexivity axiom; \Rule{And}
highlights that the first sub-goal (premise) produces an \emph{output} $V'$
which is then \emph{chained}
from one premise to another; \Rule{Inst} embodies the ``instantiation''
mechanism: in essence, if $\f y$ has not been instantiated so far, one
may instantiate it onto any other variable (rigid or flexible), i.e. add a new
entry for $\f y$ in the substitution. Finally, \Rule{Subst} may apply the
substitution at any time in order to prove the goal.

@@

    \inferrule[And]{
      V, \sigma \vdash P \dashv \sigma' \\\\
      V, \sigma' \vdash Q \dashv \sigma''
    }{
      V \vdash P \wedge Q \dashv \sigma''
    }
  \end{mathpar}
  \caption{Semi-algorithmic proof rules}
  \label{fig:proof-system}
\end{figure}

Once the proof tree has been laid out, one obtains an output (e.g. $\sigma''$ in
\Rule{And}). Since flexible variables may instantiate onto other flexible
variables, one may need to apply the substitution several times. The reflexive-transitive
closure of $\sigma$, i.e. $\sigma^*$, is thus the desired result of the proof
search.

@@

We implement proof search in OCaml (\fref{formulas}). The data type of formulas
is self-explanatory. Variables are implemented as equivalence classes in a
\emph{persistent} union-find data structure, which the module \li+P+ implements.
The $V$ parameter in our rules is embodied by the \li+state+ type; just
like the $V$ parameter is chained from one premise to another (\Rule{And}),
\li+state+ is an input and an output to the solver. Just like the $V$ parameter
in the rules, a \li+state+ of the persistent union-find represents
a set of equations between variables. In a sense, \li+state+ is a specific
implementation of the theoretical $V$ parameter. It represents a
substitution; in other words, this is what we want our solver to compute.

The choice of a persistent union-find is irrelevant. All that matters is that we
pick a data structure that models substitutions, and that is \emph{persistent}.
Had we picked an explicit substitution instead of a union-find, the rest of the
discussion would have been the same.

@@

There are two shortcomings with this solver. First, the \li+unify+ sub-routine
conflates several rules of the logic together. Indeed, the \li+return (P.union ...)+
expression hides a combination of \Rule{Inst} and \Rule{Refl}. Second, we
have no way to replay the proof to verify it independently. One may argue that
in this simplified example, one can just apply the substitution to the original
formula and verify that all the clauses are of the form $x = x$, without the
need for a proof tree. In the general case, however, the proof tree contains the
elimination witnesses for quantifiers; this allows one to independently verify a
proof without relying on inference techniques, such as flexible variables.

@@

\begin{figure}
  \centering
\begin{ocaml}
module type LOGIC = sig     module MakeProofTree (L: LOGIC) = struct
  type formula                type derivation = L.formula * rule
  type rule_name              and rule = L.rule_name * premises
end                           and premises = Premises of derivation list
                            end

module MyLogic = struct
  type formula = ... (* as before *)
  type rule_name = R_And | R_Refl | R_Inst
end
module MyProofTree = MakeProofTree(MyLogic)
\end{ocaml}
  \caption{The functor of proof trees}
  \label{fig:proof-trees}
\end{figure}

@@

module M = MOption
module MWriter = WriterT(M)(L)
\end{ocaml}
  \caption{The writer monad transformer}
  \label{fig:writer}
\end{figure}

@@

Once all the premises have been proved, one needs to draw a horizontal line and
reach the conclusion of the proof. That is, take the final state and the list of
premises, and generate a \li+derivation+ that stands for the application of the
entire rule.

@@

An outcome is, as we mentioned earlier, the pair of a final \li+state+ along
with a \li+derivation+ that justifies that we reached this state. The pair is
optional since, after all, not all formulas are provable.

@@

let prove (goal: goal) (rule: rule_name) (x: 'a m): 'a outcome =
  M.(x >>= fun (premises, state) ->
    return (state, (goal, (rule, Premises premises))))

let axiom (state: 'a) (goal: goal) (axiom: rule_name): 'a outcome =
  prove goal axiom (return state)

let fail: 'a outcome =
  M.nothing
\end{ocaml}
  \caption{The high-level combinators for building proof derivations}
  \label{fig:combinators}
\end{figure}

@@

\begin{figure}
  \centering
\begin{ocaml}
let rec prove_equality (state: state) (goal: formula) (v1: var) (v2: var) =
  let open MOption in
  match P.find v1 state, P.find v2 state with
  | Flexible, Flexible
  | Flexible, Rigid ->
      let state = P.union v1 v2 state in
      prove goal R_Instantiate begin
        premise (prove_equality state goal v1 v2) >>=
        return
      end
  (* ... *)
  | Rigid, Rigid ->
      if P.same v1 v2 state then
        axiom state goal R_Refl
      else
        fail

let rec solve (state: state) (goal: formula): state outcome =
  match goal with
  | Equals (v1, v2) ->
      prove_equality state goal v1 v2
  | And (g1, g2) ->
      prove goal R_And begin
        premise (solve state g1) >>= fun state ->
        premise (solve state g2) >>=
        return
      end
\end{ocaml}
  \caption{A solver written using the high-level combinators}
  \label{fig:solver2}
\end{figure}

@@

(* The logic is also extend with two rules. *)
type rule_name =
  (* ... *)
  | R_OrL
  | R_OrR

@@

(* Equipped with [search], we define the high-level [choice] combinator... *)
let choice (goal: goal) (args: (rule_name * 'a) list) (f: 'a -> 'b m): 'b outcome =
  M.search (fun (r, x) -> prove goal r (f x)) args

(* ...which one uses as follows: *)
let rec solve (state: state) (goal: formula): state outcome =
  match goal with
  (* ... *)
  | Or (g1, g2) ->
      choice goal [ R_OrL, g1; R_OrR, g2 ] (fun g ->
        premise (solve state g) >>=
        return
      )
\end{ocaml}
  \caption{The choice combinator}
  \label{fig:choice}
\end{figure}

@@

>>>>

\usepackage{tabularx}
\usepackage{listings}
  \def\li{\lstinline}
  \lstset{
    language=caml,
    flexiblecolumns=false,
    showstringspaces=false,
    basicstyle=\ttfamily,
    framesep=5pt,
    numberstyle=\tiny,
    numbersep=5pt,
    escapeinside={(*}{*)},
    morekeywords={above,abstract,adopts,alias,and,as,assert,begin,below,builtin,consumes,data,do,downto,duplicable,dynamic,else,empty,end,exclusive,explain,fact,fail,flex,for,from,fun,give,if,in,let,match,mutable,open,pack,perm,preserving,rec,take,taking,then,to,type,unknown,val,value,while,with,witness},
    deletekeywords={value},
  }
\usepackage{minted}
  \newminted[ocaml]{ocaml}{mathescape,fontsize=\small}
\usepackage{mathpartir}
  % Improvements to Didier's mathpartir package: make all rule names and
  % references use textsc, and also make references to rules done using the \Rule
  % command clickable in a PDF.
  % \let\TirName\textsc
  % \renewcommand{\RefTirName}[1]{\hypertarget{#1}{\TirName {#1}}}
  % \renewcommand{\DefTirName}[1]{\hyperlink{#1}{\TirName {#1}}}
  % \let\DefRule\RefTirName
  % \let\Rule\DefTirName
  \let\Rule\textsc

\newcommand{\fref}[1]{Figure~\ref{fig:#1}}
\newcommand{\sref}[1]{Section~\ref{sec:#1}}
\newcommand{\R}{\ensuremath{\mathcal{R}}} % Rigid
\newcommand{\f}[1]{\ensuremath{#1^?}} % Bold
\newcommand{\F}{\ensuremath{\mathcal{F}}} % Flexible
\newcommand{\V}{\ensuremath{\mathcal{V}}} % The prefix

@@

\section{Theory and practice}

\subsection{A minimal theory}

We are concerned with proving the validity of logical formulas; that is, with
writing a search procedure that determines whether a given goal is satisfiable.
To get started, we consider a system made up of conjunctions of equalities,
along with existential quantifiers. Any free variables are assumed to be
universally quantified. For instance, one may want to prove the following
formula:

\begin{equation}
  \exists y.\ x = y
  \label{ex1}
\end{equation}

In order to show the validity of this judgement, one will build a proof
derivation using the rules from the logic, shown in \fref{logic} ($[x/y]P$ means
``substitute $x$ with $y$ in $P$''). For instance, proving Equation \ref{ex1}
requires applying \Rule{ExistsE}, then \Rule{Refl}.

\begin{figure}
  \centering
  \begin{mathpar}
    \inferrule[Refl]{
      \quad
    }{
      x = x
    }

    \inferrule[And]{
      P \\ Q
    }{
      P \wedge Q
    }

    \inferrule[ExistsE]{
      [x/y]P
    }{
      \exists y.\ P
    }
  \end{mathpar}
  \caption{A simple logic}
  \label{fig:logic}
\end{figure}

These rules embody the Truth of our logic, i.e. an omniscient reader may use
them to show with absolute certainty that a given formula is true.
%
However, if one wants to algorithmically determine whether a given formula is
true, \Rule{ExistsE} is useless. Indeed, unless the algorithm (solver) is
equipped with superpowers, it cannot magically guess, out of the blue, a
suitable $x$ in \Rule{ExistsE} that will ensure the remainder of the derivation
succeeds. To put it another way, $x$ is a free variable (a parameter) of
\Rule{ExistsE}; the whole point of writing a proof search algorithm is to 1)
find that \Rule{ExistsE} is the right rule to apply, and 2) find that $x$ is a
suitable value for instantiating $y$, because it will make $y = x$ succeed.

Hence, in order to build a \emph{search procedure} for that logic, one will
use another set of \emph{algorithmic} rules, which hopefully enjoy:
\begin{description}
  \item[soundness]: if the algorithmic rules succeed, then there exists a
    derivation in the logic that proves the validity of the original formula,
    and
  \item[completeness]: if the algorithmic rules fail, then there exists no
    derivation in the logic that would prove the validity of the original
    formula.
\end{description}

For instance, in our logic of existentially-quantified conjunctions of
equalities, one may want to use the algorithmic rules from
\fref{proof-system}. These rules differ from \fref{logic} in that they are
algorithmic; they take an input and return an output.

@@

    \inferrule[And]{
      V, \sigma \vdash P \dashv \sigma' \\\\
      V, \sigma' \vdash Q \dashv \sigma''
    }{
      V \vdash P \wedge Q \dashv \sigma''
    }

    \inferrule[ExistsE]{
      V \uplus \f y, \sigma \vdash P \dashv \sigma'
    }{
      V, \sigma \vdash \exists y.\ P \dashv \sigma'_{|V}
    }
  \end{mathpar}
  \caption{Algorithmic proof rules}
  \label{fig:proof-system}
\end{figure}

In particular, in order to determine suitable values for the $x$ parameter in
\Rule{ExistsE}, the implementation reasons in terms of substitutions. $V$ is a
set of variables which may be substituted (recall that free variables are
considered universally quantified, hence not eligible for substitution);
variables that may be substituted are typeset as $\f y$.
The algorithm has internal state, that is, it carries a substitution $\sigma$.
Upon hitting an existential quantifier $\f y$, the algorithmic rules
\emph{open} $\f y$ and mark it as eligible for substitution. Later on (for
instance, upon hitting $\f y = x$), the algorithm may pick a
substitution for $\f y$ using \Rule{Inst}. A substitution may be applied at any
time (\Rule{Subst}). The preconditions of \Rule{Inst} guarantee that the
algorithm makes at most one choice for instantiating $\f y$.

In other words, the algorithmic rules \emph{defer} the \emph{instantiation} of
the existential quantifier until the shape of the proof obligation gives us a
\emph{hint} as to what exactly this instantiation should be. This
\emph{implementation technique} is known as \emph{flexible variables}.

The new algorithmic rules differ from the original logical rules significantly;
first, there are five rules for the algorithmic system, compared to just three
for the logical system. Second, these five rules do not map trivially to their
counterparts in the logical system. Third, these rules are only
algorithmic; the implementation that we are about to roll out uses an
optimized representation for substitutions (union-find), meaning that one not
only needs to check that the algorithmic rules are faithful to the logical
rules, but also that the implementation is faithful to the algorithmic rules.

This paper presents a library that allows one to write an implementation of the
algorithmic rules while automatically generating a derivation. The library
forces the client code to lay out premises, rule applications and
instantiations. The level of detail of the resulting derivation is left up to
the client code; they may wish to record the very compact rules from the logic,
or record more proof steps using the algorithmic rules. In any case, the
derivation serves as a proof witness; if the user wishes to do so, they can
write a validator that takes the witness and verifies that the derivation is,
indeed, correct.

The library has been used, in a preliminary form, to implement the core of the
Mezzo type-checker. This paper presents a cleaned-up, isolated version of this
library.

\subsection{An implementation with flexible variables and union-find}

The logic we present is a much simplified version of the logic (type system)
of Mezzo. In particular, this paper only mentions the right-exists quantifier;
Mezzo has all four possible combinations of left/right exists/forall. Generally,
in proof search, \emph{flexible variables} stem from the right-elimination of
existential quantifiers, or the left-elimination of universal quantifiers. The
right-elimination of universal quantifiers, or the left-elimination of
existential quantifiers give rise to universally-quantified variables, which are
called \emph{rigid}.

In order to simplify the problem, we assume that all existential variables have
been introduced as flexible variables already. That way, we won't be
sidetracked, talking about binders and the respective merits of De Bruijn
\emph{vs.} locally nameless. Furthermore, we assume that all instantiations of
flexible variables are legal. This is not true in general: for instance, if the
goal is $\forall x, \exists \f y, \forall z.\ P$, picking $\f y = z$ makes no
sense. Mezzo forbids this choice using \emph{levels}; in the present document,
we skip this discussion altogether and assume that ``all is well''. Finally,
although in a general setting, several rules may trigger for a given goal (this
is the case in Mezzo), the algorithmic set of rules we use is syntax-driven: the
syntactic shape of the goal determines which rule should be applied.

We thus restrict our formulas to conjunctions of equalities between variables.
The plan is to write a solver that takes,
as an input, a formula, and outputs a valid substitution, if any. That is,
write an algorithm that abides by the rules from \fref{proof-system}.
For instance, one may want to solve: $x = \f y \wedge z = z$.
A solution exists: the solver outputs $\sigma = \{ \f y \mapsto x \}$ as a valid
substitution that solves the input problem. However, if one attempts to solve:
$x = \f y \wedge \f y = z$, the solver fails to find a
proper substitution, and returns nothing. Indeed, the first clause demands that
$\f y$ substitutes to $x$, meaning that the second clause becomes $x = z$, which
always evaluates to false ($x$ and $z$ are two distinct rigid variables).

Once the algorithm has run, we obtain an output substitution $\sigma$. One can, if they
wish to do so, take the reflexive-transitive closure $\sigma^*$, and apply it to
a flexible variable (say, $\f y$) to recover the parameter of \Rule{ExistsE}
that should be used in the logical rules (here, $x$). This is all very informal
-- the point of the subsequent sections is to formalize the claim that the proof
search algorithm produces a proof witness.

@@

We implement proof search in OCaml (\fref{formulas}); we do not use explicit
substitutions, but rather an optimized representation based on a union-find data
structure. The data type of formulas
is self-explanatory. Variables are implemented as equivalence classes in a
\emph{persistent} union-find data structure, which the module \li+P+ implements.
The $V, \sigma$ parameters in our rules are embodied by the \li+state+ type; just
like the $\sigma$ parameter is chained from one premise to another (\Rule{And}),
\li+state+ is an input and an output to the solver. Just like the $\sigma$ parameter
in the rules, a \li+state+ of the persistent union-find represents
a set of equations between variables. In a sense, \li+state+ is a specific
implementation of the theoretical $\sigma$ parameter. It represents a
substitution; in other words, this is what we want our solver to compute.

The choice of a union-find is irrelevant. All that matters is that we
pick a data structure that models substitutions, and that is \emph{persistent}.
Had we picked an explicit substitution instead of a union-find, the rest of the
discussion would have been the same.

@@

There are two shortcomings with this solver. First, the \li+unify+ sub-routine
conflates several rules together. Indeed, the \li+return (P.union ...)+
expression hides a combination of \Rule{Inst} and \Rule{Refl}. Second, we
have no way to replay the proof to verify it independently. One may argue that
in this simplified example, the outputs substitution \emph{is} the proof
witness: one can just apply the substitution to the original
formula and verify that all the clauses are of the form $x = x$, without the
need for a proof tree. In the general case, however, the proof tree contains the
\Rule{ExistsE} rule, and proof witnesses are attached to arbitrary nodes of the
tree. We thus need to build a properly annotated proof tree in the general case.

@@

We record applications of \Rule{Inst}, \Rule{Refl} and \Rule{And}. This produces
a derivation tree that makes sure that the algorithm follows the algorithmic
rules from \fref{proof-system}. \sref{generate-logical} shows how to generate a
slightly different tree that matches the rules from \fref{logic}.

\begin{figure}
  \centering
\begin{ocaml}
(* These two modules belong to the library. *)
module type LOGIC = sig     module MakeProofTree (L: LOGIC) = struct
  type formula                type derivation = L.formula * rule
  type rule_name              and rule = L.rule_name * premises
end                           and premises = Premises of derivation list
                            end

(* This is the client code using modules from the library. *)
module MyLogic = struct
  type formula = ... (* as before *)
  type rule_name = R_And | R_Refl | R_Inst
end
module MyProofTree = MakeProofTree(MyLogic)
\end{ocaml}
  \caption{The functor of proof trees (library and client code)}
  \label{fig:proof-trees}
\end{figure}

@@

module M = MOption
module MWriter = WriterT(M)(L)
\end{ocaml}
  \caption{The writer monad transformer (library code)}
  \label{fig:writer}
\end{figure}

@@

We provide a convenience \li+qed+ combinator: once one has obtained the final
state, it pairs the state with the name of the rule we want to conclude with. It
makes the implementation of \li+solve+ (\fref{solver2}) more elegant.

Once all the premises have been proven, one needs to draw a horizontal line and
reach the conclusion of the proof. That is, take the final state and the list of
premises, and generate a \li+derivation+ that stands for the application of the
entire rule.

@@

An outcome is, as we mentioned earlier, the pair of a final \li+state+ along
with a \li+derivation+ that justifies that we reached this state. The pair is
wrapped in \li+M.t+ (here, \li+option+): proving a formula may fail.

@@

let prove (goal: goal) (x: ('a * rule_name) m): 'a outcome =
  M.(x >>= fun (premises, (state, rule)) ->
    return (state, (goal, (rule, Premises premises))))

let axiom (state: 'a) (goal: goal) (axiom: rule_name): 'a outcome =
  prove goal (return (state, axiom))

let qed r e =
  return (e, r)

let fail: 'a outcome =
  M.nothing
\end{ocaml}
  \caption{The high-level combinators for building proof derivations (library
  code)}
  \label{fig:combinators}
\end{figure}

@@

\begin{figure}
  \centering
\begin{ocaml}
let rec prove_equality (state: state) (goal: formula) (v1: var) (v2: var) =
  let open MOption in
  match P.find v1 state, P.find v2 state with
  | Flexible, Flexible
  | Flexible, Rigid ->
      let state = P.union v1 v2 state in
      prove goal begin
        premise (prove_equality state goal v1 v2) >>=
        qed R_Instantiate
      end
  (* ... *)
  | Rigid, Rigid ->
      if P.same v1 v2 state then
        axiom state goal R_Refl
      else
        fail

let rec solve (state: state) (goal: formula): state outcome =
  match goal with
  | Equals (v1, v2) ->
      prove_equality state goal v1 v2
  | And (g1, g2) ->
      prove goal begin
        premise (solve state g1) >>= fun state ->
        premise (solve state g2) >>=
        qed R_And
      end
\end{ocaml}
  \caption{A solver written using the high-level combinators (client code)}
  \label{fig:solver2}
\end{figure}

@@

(* The logic is also extended with two rules. *)
type rule_name =
  (* ... *)
  | R_OrL
  | R_OrR

@@

(* Equipped with [search], we define the [choice] library combinator... *)
let choice (goal: goal) (args: 'a list) (f: 'a -> ('b * rule_name) m): 'b outcome =
  M.search (fun x -> prove goal (f x)) args

(* ...which one uses as follows: *)
let rec solve (state: state) (goal: formula): state outcome =
  match goal with
  (* ... *)
  | Or (g1, g2) ->
      choice goal [ R_OrL, g1; R_OrR, g2 ] (fun (r, g) ->
        premise (solve state g) >>=
        qed r
      )
\end{ocaml}
  \caption{The choice combinator (library and client code)}
  \label{fig:choice}
\end{figure}

@@

\section{Generating a proof tree using the logical rules}
\label{sec:generate-logical}
